### 2010-12-28 Documentation/atropos/atropos.tex
ENH:  A few minor edits.
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@730 fd2da0a4-d968-48df-9cb5-d8c496287cbf

To highlight the
value of this open-source contribution, we performed a search of
software attributes on NITRC and found that as of November 2010 no
stand-alone EM methods are currently listed.
%Atropos's memory efficiency enables EM-segmentation of many classes at
%once, a capability that is due to a sparse internal representation of
%prior probability images that minimizes the need for random access
%memory.  
We evaluate EM-based classification of $1 mm^3$ T1 MR
neuroimages into 69 neuroanatomical regions to illustrate the practical
value of the low-memory implementation within this paper.  
Although Atropos may be applied to
multivariate data from arbitrary modalities, we limit our evaluation
to tissue-classification in T1 neuroimaging in part due to the
abundance of ``gold-standard'' data for this modality.  Consistent
with our advocacy of open science (not to mention the facilitation of
analysis due to accessibility) we also only use publicly available
data sets.  For this reason, all results in this paper are
reproducible with the caveat that users may require some guidance from
the authors or other users in the community.

@@

\subsection{Performance on Hammers Data}
Our prior work, \citep{Avants2011}, showed that the majority vote
initialization provided to Atropos by ANTs template mapping is
competitive with \cite{Heckemann2006}.  The Atropos EM extension of
improved these results further.  However, the Atropos EM segmentation
performed significantly worse.  This is not surprising, in that
Atropos EM assumes that signal from the likelihood and MRF term is
valuable in improving the segmentation.  This assumption held for
amygdala and lateral ventricles among other areas.  However, in
pallidum and corpus callosum (the most significant areas with loss of
performance), this is not true.  We believe the explanation is that
the intensity varies within these structures and that a more complex
intensity model (or finer parcellation) would be needed here.  An
alternative solution would be to use boundary conditions for these
structures, as in the PriorLabelImage Atropos option.

>>>>

To highlight the
value of this open source contribution, we performed a search of
software attributes on NITRC and found that as of November 2010 no
stand-alone EM methods are currently listed.
%Atropos's memory efficiency enables EM-segmentation of many classes at
%once, a capability that is due to a sparse internal representation of
%prior probability images that minimizes the need for random access
%memory.  
We evaluate EM-based classification of $1 mm^3$ T1 MR
neuroimages into 69 neuroanatomical regions to illustrate the practical
value of the low-memory implementation within this paper.  
Although Atropos may be applied to
multivariate data from arbitrary modalities, we limit our evaluation
to tissue-classification in T1 neuroimaging in part due to the
abundance of ``gold-standard'' data for this modality.  Consistent
with our advocacy of open science (not to mention the facilitation of
analysis due to accessibility) we also only use publicly available
data sets.  For this reason, all results in this paper are
reproducible with the caveat that users may require some guidance from
the authors or other users in the community.

@@

\subsection{Performance on Hammers Data}
Our prior work, \citep{Avants2011}, showed that the majority vote
initialization provided to Atropos by ANTs template mapping is
competitive with \cite{Heckemann2006}.  The Atropos EM extension of
improved these results further.  However, the Atropos EM segmentation
performed significantly worse.  This is not surprising, in that
Atropos EM assumes that signal from the likelihood and MRF term is
valuable in improving the segmentation.  This assumption held for
amygdala and lateral ventricles among other areas.  However, in
pallidum and corpus callosum (the most significant areas with loss of
performance), this is not true.  We believe the explanation is that
the intensity varies within these structures and that a more complex
intensity model (or finer parcellation) would be needed here.  An
alternative solution would be to use boundary conditions for these
structures, as in the {\ttfamily PriorLabelImage} Atropos initialization option.
